Use of the package \texttt{fitdistrplus} to specify a distribution from non-censored or censored data

### 2011-03-11 inst/doc/intro2fitdistrplus.Rnw
Add of maximum goodness-of-fit estimation (mgedist) and supressionof the makefile

\section{Specification of a distribution from non-censored continuous data}
%si on enlève l'étoile on a des numéros de section

\subsection{Graphical display of the observed distribution}

@@

\subsection{Characterization of the observed distribution}

@@

\subsection{Fitting of a distribution}

One or more parametric distributions may then be fitted to the data set, one at a time, using the
fonction \texttt{fitdist}. This function uses the maximum likelihood
method if the argument \texttt{method="mle"} (or if it is omitted) 
or the matching moments estimation if the argument \texttt{method="mme"}.
When fitting continuous distributions, 
Kolmogorov-Smirnov and Anderson-Darling statistics may be computed using the function \texttt{gofstat}. 
Four goodness of fit plots are also provided.

@@

In that case the Anderson-Darling test may be used to test the adequation of the distribution to data. 
<<>>=
gofstat(f1l,print.test=TRUE)
@

Generally goodness-of-fit tests may be used carefully.
In somme cases, especially on very big datasets, even if the null hypothesis is rejected a fitted distribution may be 
chosen as the best one among simple distributions to describe an empirical distribution, if the goodness-of-fit
plots do not show strong differences between empirical and theoretical distributions.

@@

Regarding the Kolmogorov-Smirnov statistic, the fit of a normal distribution seems better while regarding the 
Anderson-Darling statistic the fit of a logistic distribution seems better.
It is recommended to base the comparison of fits on the Anderson-Darling statistic when the modelling of the tails of 
a distribution is important, as it is often the case in risk assessment.

@@

\subsection{Simulation of the uncertainty by boostrap}

@@

\section{Specification of a distribution from non-censored discrete data}

@@

As for continuous distributions, one or more parametric distributions may then be fitted 
to the data set by maximum likelihood or matching moments.

@@

\section{Specification of a distribution from censored data}
%si on enlève l'étoile on a des numéros de section
Censored data may contain left censored, right censored and interval censored values, 
with several lower and upper bounds. Data must be coded into a dataframe with two columns,
 respectively named \texttt{left} 
 and \texttt{right}, describing each observed value as an interval.
 The \texttt{left} column contains either \texttt{NA} for left censored observations,
 the left bound of the interval for interval censored observations,
 or the observed value for non-censored observations.
 The \texttt{right} column contains either \texttt{NA} for right censored observations,
 the right bound of the interval for interval censored observations,
 or the observed value for non-censored observations.

\subsection{Graphical display of the observed distribution}

@@

\subsection{Fitting of a distribution}

@@

\section{Changing the optimization algorithm used to maximize the likelihood}

@@

\subsection{Changing the arguments passed to \texttt{optim}}

@@

\subsection{Supplying another optimization function}

@@

>>>>

\section{Specification of a distribution from non-censored continuous data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Graphical display of the observed distribution}
%%%%%%%%%%

@@

\subsection{Characterization of the observed distribution}
%%%%%%%%%%

@@

\subsection{Fitting of a distribution}
%%%%%%%%%%

One or more parametric distributions may then be fitted to the data set, one at a time, using the
fonction \texttt{fitdist}. This function uses the maximum likelihood
method by default or other estimation methods described in part 5 if specified in the argument \texttt{method}.
When fitting continuous distributions, 
Cramer-von Mises, Kolmogorov-Smirnov and Anderson-Darling statistics may be computed using the function \texttt{gofstat}. 
Four goodness of fit plots are also provided.

@@

In that case Cramer-von Mises and Anderson-Darling tests may be used to test the adequation of the distribution to data. 
<<>>=
gofstat(f1l,print.test=TRUE)
@

Generally goodness-of-fit tests may be used carefully.
In some cases, especially on very big datasets, even if the null hypothesis is rejected a fitted distribution may be 
chosen as the best one among simple distributions to describe an empirical distribution, if the goodness-of-fit
plots do not show strong differences between empirical and theoretical distributions.

@@

Regarding the Cramer-von Mises and Kolmogorov-Smirnov statistics, 
the fit of a normal distribution seems better while regarding the 
Anderson-Darling statistic the fit of a logistic distribution seems better.
It is recommended to base the comparison of fits on the Anderson-Darling statistic when the modelling of the tails of 
a distribution is important, as it is often the case in risk assessment.

@@

\subsection{Simulation of the uncertainty by boostrap}
%%%%%%%%%%

@@

\section{Specification of a distribution from non-censored discrete data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

As for continuous distributions, one or more parametric distributions may then be fitted 
to the data set by maximum likelihood or alternative methods described in part 5.

@@

\section{Specification of a distribution from censored data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Censored data may contain left censored, right censored and interval censored values, 
with several lower and upper bounds. Data must be coded into a dataframe with two columns,
 respectively named \texttt{left} 
 and \texttt{right}, describing each observed value as an interval.
 The \texttt{left} column contains either \texttt{NA} for left censored observations,
 the left bound of the interval for interval censored observations,
 or the observed value for non-censored observations.
 The \texttt{right} column contains either \texttt{NA} for right censored observations,
 the right bound of the interval for interval censored observations,
 or the observed value for non-censored observations.

\subsection{Graphical display of the observed distribution}
%%%%%%%%%%

@@

\subsection{Fitting of a distribution}
%%%%%%%%%%

@@

\section{Changing the optimization algorithm used to maximize the likelihood}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Changing the arguments passed to \texttt{optim}}
%%%%%%%%%%

@@

\subsection{Supplying another optimization function}
%%%%%%%%%%

@@

\section{Alternative methods to maximum likelihhod for non censored data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For non censored data, alternative methods to maximum likelihood are available.

\subsection{Moment matching estimation}
%%%%%%%%%%
Moment matching may be performed fixing the argument \texttt{method}
to \texttt{"mme"} in the call to fitdist (see the help file page of the function
\texttt{mmedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to data randomly
generated in a uniform distribution.
<<>>=
u <- runif(50,min=5,max=10)
fitdist(u,"unif",method="mme")
@

\subsection{Quantile matching estimation}
%%%%%%%%%%
Quantile matching may also be performed fixing the argument \texttt{method}
to \texttt{"qme"} in the call to fitdist and adding an argument \texttt{probs}
defining the probabilities for which the quantile matching is done.
The length of this vector must be equal
to the number of parameters to estimate.(see the help file page of the function
\texttt{qmedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to the same dataset by matching first
and third quartiles.
<<>>=
fitdist(u,"unif",method="qme",probs=c(0.25,0.75))
@

\subsection{Maximum goodness-of-fit estimation}
%%%%%%%%%%
Parameters may also be estimated by maximizing a goodness-of-fit distance
by fixing the argument \texttt{method}
to \texttt{"mge"} in the call to fitdist and adding an argument \texttt{gof}
coding for the goodness-of-fit distance chosen. One may use the classical 
Cramer-von Mises distance (\texttt{"CvM"}), the classical
Kolmogorov-Smirnov distance (\texttt{"KS"}), the classical Anderson-Darling distance (\texttt{"AD"})
which gives more weight to the tails of the distribution,
or one of the variants of this last distance (see the help file page of the function
\texttt{mgedist} in \texttt{fitdistrplus} reference manual for details).
Below is an example of fit of a uniform distribution to the same dataset by maximizing the 
Kolmogorov-Smirnov distance.
<<>>=
fitdist(u,"unif",method="mge",gof="KS")
@
